\documentclass[./main.tex]{subfiles}
\begin{document}
\section{Problem Statement}
One such application of data analytics in basketball is the classification of players into specific positions based on their attributes. Each position on the court requires a different set of skills, and players gravitate towards the positions that best match their style. As an example, taller players typically play closer to the net, where their height makes it easier for them to get rebounds and make dunks. And often, a player will start his career in one position and transition to another over time. In recent years, several prominent players have followed this trajectory. Kevin Durant, who joined the league in 2008, started as a shooting guard before later transitioning to become a power forward. Giannis Antetokounmpo, who started in 2016 as a point guard, also became a power forward later in his career.

Both of these players spent the first few years of their careers playing in a suboptimal position. Since player salaries run in the millions of dollars, coaches want to get the highest return on their investment by putting players in the position where they will perform the best. Our project attempts to examine decades of historical data in order to develop a classification model capable of accurately assigning players to their respective positions. Using this model, NBA coaches would easily be able to use a prospective player's career statistics to estimate which position they would be best suited for.

Prior to this project, we expected  certain trends—like forwards being generally taller than guards—to be reflected in the data. We presumed that we would likely discover more trends as our analysis progressed. One goal of this project was to visualize such trends by conducting clustering analysis on our data. Our aim is to show how different clusters of players vary according to different statistics. In addition, we also identify outliers that do not fit into any clusters; we predict that these outliers may correspond to certain notable players.
\end{document}